\documentclass{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{amsmath, amsfonts, amssymb, amstext, mathtools, stmaryrd, textcomp, xcolor, graphicx, tikz}
\usepackage[hidelinks]{hyperref}
\usetikzlibrary{automata, positioning, arrows, trees}
\tikzset{->,>=stealth,
every state/.style={thick, fill=gray!10}, 
initial text=$ $,
}
\newcommand{\e}{\varepsilon}
\newcommand{\s}{\Sigma}
\newcommand{\g}{\Gamma}
\newcommand{\so}{\rightarrow}
\newcommand{\str}{\texttt}
\newcommand{\newp}{\\[2mm]}
\newcommand{\defeq}{\coloneqq}
\newcommand{\spc}{\textvisiblespace}

\title{Homework 05}
\author{Aaron Wang}
\date{March 21 2025}

\begin{document}
\maketitle
\begin{enumerate}
    \item \textbf{Non-closure properties of CFLs}
    \begin{enumerate}
        \item [(a)][Exercise 2.2a] Use the languages
        \[
            A=\{\str{a}^m\str{b}^n\str{c}^n|m,n \geq 0\}
        \]
        \[
            B=\{\str{a}^n\str{b}^n\str{c}^m|m,n \geq 0\}
        \]
        to prove that context-free languages are not closed under intersection. \newp
        \input{HW05/1.a}
        \item [(b)][Exercise 2.2b] Use Problem 1a and DeMorgan’s law to prove that context-free languages are \textit{not} closed under complementation. \newp
        \input{HW05/1.b}
    \end{enumerate}
\newpage
    \item \textbf{There and back again.} Imagine a robot turtle that you can give instructions \str{u} (go up 1 cm), \str{d} (go down 1 cm), \str{l} (go left 1 cm), \str{r} (go right 1 cm). A program is a string of instructions.\newp
    Let $C$ be the set of programs that make the turtle return to its starting point. For example, \str{uurdrdll} is in $C$, as shown in this picture:
    \input{HW05/2.figure}
    \vspace{-10mm}
    \begin{enumerate}
        \item Prove that $C$ is not context-free.\newp
        \input{HW05/2.a}
        \item Write a \textbf{formal description} of a Turing machine that decides $C$.\newp
        \input{HW05/2.b}
    \end{enumerate}
\newpage
    \item \textbf{Turing closure properties.} Let $\s = \{\str{0}, \str{1}\}$. Recall in HW2 we defined
        \[
        \text{STRETCH}(w_1w_2 \cdots w_n) = w_1w_1w_2w_2 \cdots w_{n-1}w_{n-1}w_nw_n. 
        \]
        for any string $w_1w_2 \cdots w_n \in \s^*$ This induces an operation on languages,
        \[
        \text{STRETCH}(L) = \{\text{STRETCH}(w) | w \in L\}.  
        \]

    \begin{enumerate}
        \item Write an \textbf{implementation-level} description of a Turing machine $S$ that, on input $v \in \s^*$, decides whether $v = \text{STRETCH}(u)$ for some $u$. Moreover, if $S$ accepts $v$, then when it halts, the contents of the tape should be $u$. For example, if the input is \str{001100}, $S$ should accept and the final contents of the tape should be \str{010}. But if the input is \str{001101}, $S$ should reject.\newp
        \input{HW05/3.a.tex}
        \item Prove that if $L$ is a Turing-decidable language over $\s$, then STRETCH$(L)$ is also Turing-decidable. You should let $M$ be a Turing machine that decides $L$, then use your answer to 3a to give an \textbf{implementation-level} description of a Turing machine that decides STRETCH$(L)$. One of the lines of your description can be ``Simulate $M$.''\newp
        \input{HW05/3.b.tex}
        \item Prove that if $L$ is a Turing-recognizable language, then STRETCH$(L)$ is also Turing-recognizable.\newp
        \input{HW05/3.c.tex}
    \end{enumerate}
\end{enumerate}
\end{document}